Linear instability underlying synchronous waving of marine grass in flow

### 2014-09-07 Paper/grass.tex
minor update from shreyas

%<<<<<<< HEAD
% A threshold in $\Rey$ for the onset of the instability naturally emerges from the solution of \eqref{Orr-somerfield}. 
% The primary reason for the existence of critical $\Rey$ is the presence of dissipation of flow instability 
% due to grass drag. Indeed a calculation undertaken for terrestrial canopy shows the suppression of growth rate of instability
% due to grass drag\cite{Delangre06}. Absence of threshold in the previous analysis can be attributed to the assumptions such 
% as approximationn of mean flow with the free shear layer profile and the exclusion of grass drag in the stability analysis 
% \cite{Raupach96,Delangre06}.
% The dependence of this critical $\Rey$, and the corresponding fastest growing wavenumber $k$, 
% on the $\delta/H$ and $\hg/H$ is shown in figure \ref{Re_vs_delta}, and compared with experimental observation of the 
% threshold\cite{Ghisal02}. The good agreement between predicted and estimated threshold suggest that the grass drag plays a 
% crucial role in setting up the flow instability.
% 
% Comparison of frequency (Im$(\sigma)$) of the fastest growing mode with that of experimental observations of frequencies in the lab scale experiments, for cases where the vegetation was sufficiently dense to be modeled by a continuum drag field, is also shown in 
% Figure \ref{Re_vs_delta}. The observed frequencies are associated with the peaks in velocity spectra, frequency of monami and frequency of vortex passage \cite{Ghisal02}\shreyas{cite someone}. The deviation of predicted frequency from the observed may be attributed to the various 
% simplification we have made in our model. In a real canopy, the drag coefficients are known to
% vary from bottom to tip of the grass blades\cite{Vivoni98,Nepf00}. The turbulent viscosity is also known to vary between the flow of unvegetated region and flow through the canopy\cite{Ghisal02}. Although these variation
% are not central to the mechanism leading to the instability of flow, we believe an improved analysis of flow with these variation in the model might lead to a better agreement between the
% observed frequency and the predicted frequency.
% =======
Comparison of frequency (Im$(\sigma)$) of the fastest growing mode with that of experimental observations of frequencies in
the lab scale experiments, for cases where the vegetation was sufficiently dense to be modeled by a continuum drag field, 
is also shown in Figure \ref{Re_vs_delta}. 
The observed frequencies are associated with the peaks in velocity spectra, frequency of \monami and frequency of 
vortex passage \cite{Ghisal02}, and compare well with the predicted frequencies.

>>>>

%<<<<<<< HEAD
% A threshold in $\Rey$ for the onset of the instability naturally emerges from the solution of \eqref{Orr-somerfield}. 
% The primary reason for the existence of critical $\Rey$ is the presence of dissipation of flow instability 
% due to grass drag. Indeed a calculation undertaken for terrestrial canopy shows the suppression of growth rate of instability
% due to grass drag\cite{Delangre06}. Absence of threshold in the previous analysis can be attributed to the assumptions such 
% as approximationn of mean flow with the free shear layer profile and the exclusion of grass drag in the stability analysis 
% \cite{Raupach96,Delangre06}.
% The dependence of this critical $\Rey$, and the corresponding fastest growing wavenumber $k$, 
% on the $\delta/H$ and $\hg/H$ is shown in figure \ref{Re_vs_delta}, and compared with experimental observation of the 
% threshold\cite{Ghisal02}. The good agreement between predicted and estimated threshold suggest that the grass drag plays a 
% crucial role in setting up the flow instability.
% 
% Comparison of frequency (Im$(\sigma)$) of the fastest growing mode with that of experimental observations of frequencies in the lab scale experiments, for cases where the vegetation was sufficiently dense to be modeled by a continuum drag field, is also shown in 
% Figure \ref{Re_vs_delta}. The observed frequencies are associated with the peaks in velocity spectra, frequency of monami and frequency of vortex passage \cite{Ghisal02}\shreyas{cite someone}. The deviation of predicted frequency from the observed may be attributed to the various 
% simplification we have made in our model. In a real canopy, the drag coefficients are known to
% vary from bottom to tip of the grass blades\cite{Vivoni98,Nepf00}. The turbulent viscosity is also known to vary between the flow of unvegetated region and flow through the canopy\cite{Ghisal02}. Although these variation
% are not central to the mechanism leading to the instability of flow, we believe an improved analysis of flow with these variation in the model might lead to a better agreement between the
% observed frequency and the predicted frequency.
% =======
Comparison of frequency (Im$(\sigma)$) of the fastest growing mode with that of experimental observations of frequencies in
the lab scale experiments, for cases where the vegetation was sufficiently dense to be modeled by a continuum drag field, 
is shown in Figure \ref{Re_vs_delta}. 
The observed frequencies are associated with the peaks in velocity spectra, frequency of $\monami$ and frequency of 
vortex passage \cite{Ghisal02}, and compare well with the predicted frequencies.
